get_sen
title: "Sentiment Analysis"
output: html_notebook
---

Sentiment data

```{r}
library(tidytext)
str(sentiments)
```

```{r}
summary(sentiments)
```

The sentiments data consists of lexicons from three sources:

- [NRC Word-Emotion Association Lexicon](http://saifmohammad.com/WebPages/NRC-Emotion-Lexicon.htm)
- [Bing](https://www.cs.uic.edu/~liub/FBS/sentiment-analysis.html)
- [AFINN](http://www2.imm.dtu.dk/pubdb/views/publication_details.php?id=6010)

```{r}
get_sentiments('nrc')
```


```{r}
get_sentiments('bing')
```

```{r}
get_sentiments('afinn')
```


Each sentiment lexicon can be used in a different manner.

**Shakespeare's work:**
- Comedy: Much Ado About Nothing (Gutenberg's ID: 1519)
- Tragedy: Romeo and Juliet (Gutenberg's ID: 1112)

```{r}
library(gutenbergr)
library(dplyr)

comedy <- gutenberg_download(1519)
tragedy <- gutenberg_download(1112)

tidy_comedy <- comedy %>%
  unnest_tokens(sentence, text, token = 'sentences') %>%
  mutate(line_number = row_number()) %>%
  unnest_tokens(word, sentence) %>%
  anti_join(stop_words) %>%
  mutate(title = 'Much Ado About Nothing')

tidy_tragedy <- tragedy %>%
  unnest_tokens(sentence, text, token = 'sentences') %>%
  mutate(line_number = row_number()) %>%
  unnest_tokens(word, sentence) %>%
  anti_join(stop_words) %>%
  mutate(title = 'Romeo and Juliet')

tidy_shakespeare <- rbind (tidy_comedy, tidy_tragedy)
```

**"Small sections of text may not have enough words to get a good estimate of sentiment while really 
large sections can wash out narrative structure (balancing out sentiments)"**



```{r}
shakespeare_sentiment_bing <- tidy_shakespeare %>%
  inner_join(get_sentiments('bing')) %>%
  count(title, index = line_number %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
```


```{r}
library(ggplot2)

ggplot(shakespeare_sentiment_bing, aes(index, sentiment, fill = title)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~title, ncol = 2, scales = "free_x")
```



** Challenge **

Select a 1-star review from `df_emerils` and identify its sentiment using the `bing` sentiment data. 

```{r}

```

Select a 5-star review from `df_emerils` and identify its sentiment using the `bing` sentiment data. 

```{r}

```

Using the `nrc` sentiment data, we have another perspective in analyzing sentiments

```{r}
shakespeare_sentiment_nrc <- tidy_shakespeare %>%
  inner_join(get_sentiments('nrc')) %>%
  count(title, index = line_number %/% 80, sentiment)
```

```{r}
library(ggplot2)

ggplot(shakespeare_sentiment_nrc, aes(index, n)) +
  geom_col(show.legend = TRUE) +
  geom_smooth() + 
  facet_grid(title ~ sentiment)
```



** Challenge (15 minutes) **

Aggregate all reviews into corresponding star-ratings (1 through 5). Study the 10 NRC sentiments for each rating scale. 

```{r}


```











