---
title: "Word and Document Frequency"
output: html_notebook
---

**Quantification of a document's contents and meanings**

- Can we *quantitatively infer* the contents and meanings of a document by looking at the *words* that make up the document?

- Does the frequency of a word, called *term frequency (tf)* (i.e., how frequently a word occurs in a document), express how importance this word is in a document (thus providing an insight into the author's intention when using that word).
  - How do you account for frequently used words (e.g., the, is, of ...)?
- Another metric is the *inverse document frequency (idf)*, which represents the reduction of weight for commonly used word (across a set of documents) and increase of weight for words that are used less frequently (perhaps more unique to individual documents). 
- *tf-idf*, a combination of two metrics, measure the importance of a word to a document in a collection (*corpus*) of documents. 


How can we further quantify the meanings of Emerils' reviews with respects to rating scores?

```{r}
library(dplyr)
library(tidytext)

data_dir <- 'data'
restaurant_dir <- 'emerils'

input_files <- list.files(file.path(data_dir,
                                    restaurant_dir),
                          full.names = TRUE)

file_names <- list.files(file.path(data_dir,
                                   restaurant_dir))

dates <- c()
reviews <- c()
ratings <- c()

for (i in 1:length(file_names)){
    current_page <- read_html(input_files[i])
    current_revs <- xml_find_all(current_page, "//div[@itemprop='review']")
    list_revs <- as_list(current_revs)
    count_revs <- length(list_revs)
    for (j in 1:count_revs){
        review_date <- attr(list_revs[[j]][[5]],'content') # Review Date
        review_rating <- as.numeric(attr(list_revs[[j]][[3]][[2]],'content')) # Review Rating
        review_contents <- list_revs[[j]][[6]][[1]]
        
        dates <- c(dates, review_date)
        ratings <- c(ratings, review_rating)
        reviews <- c(reviews, review_contents)
    }
}

df_emerils <- data.frame(Date = dates,
                         Rating = ratings,
                         Review = reviews, stringsAsFactors = FALSE)
```

We first need to break the reviews down to a tidy text format:

```{r}
tidy_emerils <- df_emerils %>%
  unnest_tokens(word, Review) %>%
  anti_join(stop_words) %>%
  count(Rating, word, sort = TRUE) %>%
  ungroup()

total_words <- tidy_emerils %>%
  group_by(Rating) %>%
  summarize(total = sum(n))

tidy_emerils <- left_join(tidy_emerils, total_words)
```


The library `tidytext` provides a convenient function called `bind_tf_idf` to calculate *tf*, *idf*, and *td-idf*. 

```{r}
tidy_emerils <- tidy_emerils %>%
  bind_tf_idf(word, Rating, n)

tidy_emerils %>%
  arrange(word)
```



```{r}
tidy_emerils %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>% 
  group_by(Rating) %>% 
  top_n(15) %>% 
  ungroup %>%
  ggplot(aes(word, tf_idf, fill = Rating)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~Rating, ncol = 2, scales = "free") +
  coord_flip()
```





